Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-08 writeup/gz_hubble_data.tex
Text and Fig 10 fixes for #66.

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The user weighting $(w)$ is 1 for the top 95\% of users as ranked by consistency. For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF. Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal. This method is primarily effective, however, at filtering out contributions from random or delibrately malicious classifiers.

@@

The GZH decision tree has four broad sets of morphologies classified by the users. The first option is designating the object as a star or artifact (the result of either bad data or incorrect classification by the ACS pipeline as a galaxy); in this case, the classification ends and no further questions are asked. The second set are smooth galaxies, intended to identify ellipticals/early-types; users also measure the relative axial ratio (roundness) for these galaxies. The third set is for disk/late-type galaxies, which measures the features necessary to place a galaxy on the standard Hubble tuning fork (bars, spiral arm, strength of the central bulge). The final set, which is new to the high-redshift targets in GZH, asks users to identify objects dominated by clumpy morphologies. Further annotation for these galaxies includes assessing the number, arrangement, relative brightness, and location of the clumps within the galaxy. Finally, every classification of a galaxy gives users the option of annotating ``odd'' features within the image; these labels are typically rare in large surveys, including dust lanes, gravitational lenses, and major mergers.

The number of independent classifications per subject collected by GZH is on average higher than GZ1 or GZ2, due to both the increased complexity of the decision tree and the relative difficulty of classifying images of small and distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets have a median of 122~independent classifications per image. The remainder of the images were set slightly lower, either from having a later activation date (COSMOS, simulated AGN) or by setting a lower retirement rate (the low-redshift SDSS Stripe~82 galaxies). Images from these samples have a median of 46-48~classifications per image (Figure~\ref{fig:classification_hist}).

@@

%\begin{table*}
%\center
%\caption{Summary of morphological categories selected for \ferengi{} sample.\label{tbl:morphologies}}
%\begin{tabular}{lllc}
%\hline\hline
%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
%\hline
%Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
%                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
%                    & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
%Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
%                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
%                    & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
%Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
%                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
%                    & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
%Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
%                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
%                    & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
%Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
%                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
%                    & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
%Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
%                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
%                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
%Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
%                    & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
%                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
%\hline\hline
%\end{tabular}
%\end{table*}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/example_ferengi.pdf}
\caption{Examples of two galaxies which have been run through the \ferengi{} code to produce simulated \hst{} images. The measured value of \pfeatures{} from GZH for the images in each panel are (1) Top row: \pfeatures~= (0.900, 0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \pfeatures~= (1.000, 0.875, 0.875, 0.625, 0.375). \label{fig:exampleFERENGI}}
\end{figure*}

@@

\begin{figure*}
\centering
\subfigure{[a]\label{fig:6a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
\subfigure{[b]\label{fig:6b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
\\
\subfigure{[c]\label{fig:6c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
\subfigure{[d]\label{fig:6d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
\caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample. [a]: Each point in a given redshift and surface brightness bin represents a unique galaxy. On the $y$-axis in each bin is the \pfeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin. On the $x$-axis is the \pfeatures{} value of the image of the same galaxy redshifted to $z=0.3$. The dashed black lines represent the best-fit polynomials to the data in each square. The solid black line represents \pfeaturesz=\pfeaturesrest. Regions in which there is a single-valued relationship between \pfeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray. [b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. [c]: The same data as [a] is shown. Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \pfeaturesrest{} for a given range of observed \pfeaturesz{} values. In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values. [d]: The same data as [b], but highlighting the upper and lower limit regions.}
\label{fig:p_vs_p}
\end{figure*}

Figure~\ref{fig:p_vs_p} shows the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images. For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, \pfeaturesz, the value measured at that simulated redshift, is plotted against \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.

The objective is to use these data to predict, for a galaxy with a measured \pfeaturesz{} value, what its \pfeatures{} value \emph{would have been} if it had been viewed at $z=0.3$. This predicted value is defined as the debiased vote fraction \pfeaturesdebiased, and is calculated by applying a correction to the measured value of \pfeatures, determined by the $\zeta$ function described in the previous section. A reliable predicted value can be obtained so long as the relationship between \pfeaturesz{} and \pfeaturesrest{} is single-valued; that is, for a given \pfeaturesz, there is exactly one corresponding value of \pfeatures{} at $z=0.3$.

Figure~\ref{fig:p_vs_p} shows that the relationship between \pfeaturesz{} and \pfeaturesrest{} is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/\pfeatures{} space. These regions tend to have low \pfeatures{} values at high redshift, but a wide range of values at $z=0.3$. These regions contain two morphological types of galaxies: the first set are genuine ellipticals, which have low values of \pfeatures{} at both high and low redshift. The second group are disks whose features become indistinct at high redshift; hence their \pfeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low. This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.

The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \pfeaturesz{} and \pfeaturesrest{} is modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and using the best fit out of the three. These fits are shown as the dashed black lines in Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; this is quantified by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \pfeaturesz{} cannot be boosted to its \pfeaturesrest{} value. Galaxies in this region are referred to as the \emph{lower limit} sample. These regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently high slopes to consider the relationship as single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies are considered to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the debiased correction to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \pfeatures{}. To define this smooth space, a convex hull is generated that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. The resulting hulls define the correctable and lower-limit regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than $z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot have the potential for a correction determined, due either a lack of redshift for the host galaxy or insufficient \ferengi{} images corresponding to the relevant $z$-$\mu$ values.

For the ``lower-limit'' galaxies for which a single debiased \pfeatures{} value cannot be confidently assigned, the \emph{range} of debiased values is estimated using a method visualized in Figure~\ref{fig:6c}. This uses the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift. Each $z$,$\mu$ bin, shows the spread of intrinsic values of \pfeaturesrest{} for four ranges of observed \pfeatures. The range of intrinsic values is defined as the inner 80\% of the data, represented by the orange bars in Figure~\ref{fig:6c}. For any galaxy which cannot be directly debiased by the $\zeta$ method, these ranges are used to denote the upper and lower limits on the expected values \pfeaturesrest{} as a function of the observed \pfeatures.

\begin{table}
\center
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images have a single-valued relationship between their measured \pfeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Images with only a lower-limit on \pfeatures{} have a non single-valued relationship (blue regions). NEI (``not enough information'') images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Lower-limit                        & 1,986   & 50\% \\
NEI                                & 80      &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
\label{fig:debiased_corrections}
\end{figure*}

Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{fig:debiased_corrections}). As a check, highly boosted galaxies are compared to the expert classifications in the CANDELS catalog \citep{kar15}. There are only eight galaxies that were strongly boosted ($p_\mathrm{features,raw}<0.2$ and $p_\mathrm{features,best} > 0.5$) in GZH and also appears in the CANDELS expert sample. Of those eight galaxies, \citet{kar15} classifies 5 as spheroids, 2 as disks, and 1 as irregular/disky. The \pbest{} values for GZH are all between 0.5 and 0.6, making them intermediate disk candidates. One of the spheroids has hints of an interaction or minor merger to the south that may have been missed by the CANDELS experts, but almost all images are dim and with very low surface brightnesses in the ACS imaging, making positive identification challenging. Since the surveys use different rest-frame filters and the overlap sample is tiny, though, detailed comparisons between the overall morphologies are highly difficult.

\subsection{Challenges of debiasing questions beyond ``smooth or features''}
\label{ssec:higher_order_tasks}
As with the HST images, each \ferengi{} subject has a varying number of users answering the various questions in the hierarchical decision tree. Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions $p_\mathrm{smooth}, p_{features}$, and $p_\mathrm{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}). The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question. The average number of responses per task for fourth- or fifth-tier questions such as spiral arm structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this is distribution is strongly bimodal (reflecting the true morphologies of selected galaxies), the very low absolute numbers of votes introduce very high variance when attempting to calculate a statistical correction.

In the \ferengi{} data, these numbers severely limit the amount of information that can be extracted for the higher-tier questions. The debiasing technique used (Section~\ref{ssec:zeta}) requires that at least 10~users answer each question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding image at higher redshift. This requirement is (by default) met by all galaxies for the smooth/features question. However, this is often \emph{not} met for questions beyond Task~01; on average. $60\%\pm24\%$ of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% achieved for Task~01 (Table~\ref{tbl:ferengi_corrections}). Of the remaining \ferengi{} galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01. The goodness-of-fit was evaluated in each bin, for each Task, using a normalized $\chi^2$ metric. The mean $\chi^2$ for all higher-order tasks was $0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$. Based on this statistic, the data cannot not be modeled with sufficient confidence for the higher order tasks. An example of the debiasing technique applied to $p_{\rm bar}$ is shown in Section~\ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:p_vs_p_bar} confirms that the points in each bin are scattered to a degree at which no strong correlation is present. For these reasons, debiased vote fractions are only offered in the GZH catalog for Task~01 (smooth/features).

>>>>

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each response to a question ($f_{response}$) on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The user weighting $(w)$ is 1 for the top 95\% of users as ranked by consistency. For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF. Since this only affects a tiny percentage of the users (and an even smaller percentage of the classifications) the overall effect on the GZH dataset is minimal. This method is effective, however, at filtering out contributions from random or delibrately malicious classifiers.

@@

The GZH decision tree has four broad sets of morphologies classified by the users. The first option is designating the object as a star or artifact (the result of either bad data or incorrect classification by the ACS pipeline as a galaxy); in this case, the classification ends and no further questions are asked. The second set are smooth galaxies, intended to identify ellipticals/early-types; users also measure the relative axial ratio (roundness) for these galaxies. The third set is for disk/late-type galaxies, which measures the features necessary to place a galaxy on the standard Hubble tuning fork (bars, spiral arm, strength of the central bulge). The final set, which is new to the high-redshift targets in GZH, asks users to identify objects dominated by clumpy morphologies. Further annotation for these galaxies includes assessing the number, arrangement, relative brightness, and location of the clumps within the galaxy. Finally, every classification of a galaxy gives users the option of annotating ``odd'' features within the image; these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust lanes, gravitational lenses, and major mergers.

The number of independent classifications per subject collected by GZH is on average higher than GZ1 or GZ2, due to both the increased complexity of the decision tree and the relative difficulty of classifying images of small and distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets have a median of 122~independent classifications per image. The remainder of the images either had a later activation date (COSMOS, simulated AGN) or by a lower retirement limit (the low-redshift SDSS Stripe~82 galaxies). Images from these samples have a median of 46-48~classifications per image (Figure~\ref{fig:classification_hist}).

@@

%\begin{table*}
%\center
%\caption{Summary of morphological categories selected for \ferengi{} sample.\label{tbl:morphologies}}
%\begin{tabular}{lllc}
%\hline\hline
%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
%\hline
%Features            & Yes       & $f_{\rm features} > 0.8$, $f_{\rm odd} < 0.1$                                                         & 12 \\ 
%                    & Int.      & $0.3 < f_{\rm smooth} < 0.6$, $f_{\rm odd} < 0.1$                                                     & 12 \\ 
%                    & No        & $f_{\rm smooth} > 0.8$, $f_{\rm odd} < 0.1$                                                           & 12 \\ 
%Merger              & No        & $f_{\rm features} > 0.8$, $f_{\rm odd < 0.1}$, $f_{\rm merger} < 0.1$                                 & 12 \\
%                    & Int.      & $f_{\rm odd} > 0.5$, $0.1< f_{\rm merger} < 0.4$                                                      & 12 \\ 
%                    & Yes       & $f_{\rm odd} > 0.5$, $f_{\rm merger} > 0.4$                                                           & 12 \\
%Edge-on             & Yes       & $f_{\rm edgeon} > 0.8$, $f_{\rm features} > 0.5$                                                      & 12 \\
%                    & Int.      & $0.4 < f_{\rm edgeon} < 0.8$ , $f_{\rm features} > 0.5$                                               & 12 \\
%                    & No        & $f_{\rm edgeon} < 0.2$, $f_{\rm features} > 0.5$                                                      & 12 \\
%Bar                 & No        & $f_{\rm bar} < 0.1$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
%                    & Int.      & $0.2 < f_{\rm bar} < 0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                           & 24 \\
%                    & Yes       & $f_{\rm bar} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
%Visible spiral      & No        & $f_{\rm spiral} < 0.2$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
%                    & Int.      & $0.2 < f_{\rm spiral} < 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$   & 12 \\
%                    & Yes       & $f_{\rm spiral} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
%Oblique bulge size  & No        & $f_{\rm nobulge>0.6}$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$          & 12 \\
%                    & Int.      & $f_{\rm justnoticeable}>0.6$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$   & 12 \\
%                    & Yes       & $f_{\rm obvious|dominant}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$ & 12 \\
%Edge-on bulge shape & Round     & $f_{\rm rounded}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
%                    & Boxy      & $f_{\rm boxy}>0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.2$                                  & 12 \\
%                    & No bulge  & $f_{\rm nobulge}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
%\hline\hline
%\end{tabular}
%\end{table*}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/example_ferengi.pdf}
\caption{Examples of two galaxies which have been run through the \ferengi{} code to produce simulated \hst{} images. The measured value of \ffeatures{} from GZH for the images in each panel are (1) Top row: \ffeatures~= (0.900, 0.625, 0.350, 0.350, 0.225) and (2) Bottom row: \ffeatures~= (1.000, 0.875, 0.875, 0.625, 0.375). \label{fig:exampleFERENGI}}
\end{figure*}

@@

\begin{figure*}
\centering
\subfigure{[a]\label{fig:6a}\includegraphics[width=0.5\textwidth]{figures/p_vs_p_SB_redshift.pdf}}
\subfigure{[b]\label{fig:6b}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot1.pdf}}
\\
\subfigure{[c]\label{fig:6c}\includegraphics[width=0.5\textwidth]{figures/orangebars.pdf}}
\subfigure{[d]\label{fig:6d}\includegraphics[width=0.4\textwidth]{figures/z1_mu20_subplot2.pdf}}
\caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample. [a]: Each point in a given redshift and surface brightness bin represents a unique galaxy. On the $y$-axis in each bin is the \ffeatures{} value of the image of that galaxy redshifted to the value corresponding to that redshift bin. On the $x$-axis is the \ffeatures{} value of the image of the same galaxy redshifted to $z=0.3$. The dashed black lines represent the best-fit polynomials to the data in each square. The solid black line represents \ffeaturesz=\ffeaturesrest. Regions in which there is a single-valued relationship between \ffeatures{} at high redshift and at $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray. [b]: A larger version of the dark-outlined square in [a], containing \ferengi{} galaxies that have been artificially redshifted to $z=1.0$ and have surface brightnesses between $20.3 < \mu < 21.0$ $\rm (mag/arcsec^2)$. [c]: The same data as [a] is shown. Each $z,\mu$ bin is divided into 4 sub-bins to determine the range of intrinsic \ffeaturesrest{} for a given range of observed \ffeaturesz{} values. In each sub-bin, the orange bars represent the inner 80$^\mathrm{th}$ percentiles of the data, the boundaries of which are the lower and upper limits of the debiased values. [d]: The same data as [b], but highlighting the upper and lower limit regions.}
\label{fig:f_vs_f}
\end{figure*}

Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images. For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, \ffeaturesz, the value measured at that simulated redshift, is plotted against \ffeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.

The objective is to use these data to predict, for a galaxy with a measured \ffeaturesz{} value, what its \ffeatures{} value \emph{would have been} if it had been viewed at $z=0.3$. This predicted value is defined as the debiased vote fraction \ffeaturesdebiased, and is calculated by applying a correction to the measured value of \ffeatures, determined by the $\zeta$ function described in the previous section. A reliable predicted value can be obtained so long as the relationship between \ffeaturesz{} and \ffeaturesrest{} is single-valued; that is, for a given \ffeaturesz, there is exactly one corresponding value of \ffeatures{} at $z=0.3$.

Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and \ffeaturesrest{} is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/\ffeatures{} space. These regions tend to have low \ffeatures{} values at high redshift, but a wide range of values at $z=0.3$. These regions contain two morphological types of galaxies: the first set are genuine ellipticals, which have low values of \ffeatures{} at both high and low redshift. The second group are disks whose features become indistinct at high redshift; hence their \ffeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low. This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.

The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \ffeaturesz{} and \ffeaturesrest{} is modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and using the best fit out of the three. These fits are shown as the dashed black lines in Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \ffeaturesz{} and \ffeaturesrest; this is quantified by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \ffeaturesz{} cannot be boosted to its \ffeaturesrest{} value. Galaxies in this region are referred to as the \emph{lower limit} sample. These regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently high slopes to consider the relationship as single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies are considered to have ``not enough information'' to determine the \ffeaturesz{} and \ffeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \ffeatures{} a galaxy must have in order for the debiased correction to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \ffeatures{}. To define this smooth space, a convex hull is generated that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\ffeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. The resulting hulls define the correctable and lower-limit regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than $z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot have the potential for a correction determined, due either a lack of redshift for the host galaxy or insufficient \ferengi{} images corresponding to the relevant $z$-$\mu$ values.

For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value cannot be confidently assigned, the \emph{range} of debiased values is estimated using a method visualized in Figure~\ref{fig:6c}. This uses the \ferengi{} simulated data to analyze the range of intrinsic \ffeaturesrest{} values for any given observed \ffeatures{} value, again as a function of surface brightness and redshift. Each $z$,$\mu$ bin, shows the spread of intrinsic values of \ffeaturesrest{} for four ranges of observed \ffeatures. The range of intrinsic values is defined as the inner 80\% of the data, represented by the orange bars in Figure~\ref{fig:6c}. For any galaxy which cannot be directly debiased by the $\zeta$ method, these ranges are used to denote the upper and lower limits on the expected values \ffeaturesrest{} as a function of the observed \ffeatures.

\begin{table}
\center
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:f_vs_f}. Correctable images have a single-valued relationship between their measured \ffeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:f_vs_f}). Images with only a lower-limit on \ffeatures{} have a non single-valued relationship (blue regions). NEI (``not enough information'') images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Lower-limit                        & 1,986   & 50\% \\
NEI                                & 80      &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased \ffeatures{} corrected to $z=0.3$ vs weighted \ffeatures{} for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
\label{fig:debiased_corrections}
\end{figure*}

Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{fig:debiased_corrections}). As a check, highly boosted galaxies are compared to the expert classifications in the CANDELS catalog \citep{kar15}. There are only eight galaxies that were strongly boosted (\ffeatures$<0.2$ and \fbest$>0.5$) in GZH and also appears in the CANDELS expert sample. Of those eight galaxies, \citet{kar15} classifies 5 as spheroids, 2 as disks, and 1 as irregular/disky. The \fbest{} values for GZH are all between 0.5 and 0.6, making them intermediate disk candidates. One of the spheroids has hints of an interaction or minor merger to the south that may have been missed by the CANDELS experts, but almost all images are dim and with very low surface brightnesses in the ACS imaging, making positive identification challenging. Since the surveys use different rest-frame filters and the overlap sample is tiny, though, detailed comparisons between the overall morphologies are highly difficult.

\subsection{Challenges of debiasing questions beyond ``smooth or features''}
\label{ssec:higher_order_tasks}
As with the HST images, each \ferengi{} subject has a varying number of users answering the various questions in the hierarchical decision tree. Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and \fartifact{} are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}). The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question. The average number of responses per task for fourth- or fifth-tier questions such as spiral arm structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this is distribution is strongly bimodal (reflecting the true morphologies of selected galaxies), the very low absolute numbers of votes introduce very high variance when attempting to calculate a statistical correction.

In the \ferengi{} data, these numbers severely limit the amount of information that can be extracted for the higher-tier questions. The debiasing technique used (Section~\ref{ssec:zeta}) requires that at least 10~users answer each question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding image at higher redshift. This requirement is (by default) met by all galaxies for the smooth/features question. However, this is often \emph{not} met for questions beyond Task~01; on average. $60\%\pm24\%$ of the galaxies do not have sufficient data to measure a correction, as compared to 2.0\% achieved for Task~01 (Table~\ref{tbl:ferengi_corrections}). Of the remaining \ferengi{} galaxies which did meet this requirement, polynomials were fit to the data in each redshift-surface brightness bin, as was done for Task~01. The goodness-of-fit was evaluated in each bin, for each Task, using a normalized $\chi^2$ metric. The mean $\chi^2$ for all higher-order tasks was $0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$. Based on this statistic, the data cannot not be modeled with sufficient confidence for the higher order tasks. An example of the debiasing technique applied to \fbar{} is shown in Section~\ref{sec:ferengi_bar}; visual inspection of Figure~\ref{fig:f_vs_fbar} confirms that the points in each bin are scattered to a degree at which no strong correlation is present. For these reasons, debiased vote fractions are only offered in the GZH catalog for Task~01 (smooth/features).
